\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[german]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\parindent 0pt
\author{Maike Maas, Valerie Poser, Sebastian Becking,\\
Marc Jose, Fabian Kosmale, Heiko Becker}
\title{Visualizing commit comments with chromograms}
\begin{document}
\maketitle
\renewcommand{\baselinestretch}{1.50}\normalsize
\section{Must-Haves:}
\begin{enumerate}
\item The products front end is a website working with recent and well known browsers (e.g. Firefox, Google Chrome, latest release of Firefox, Opera, Safari, mobile Versions of those).
\item It supports visualization of the structure of git repositorys from a given URL.
\item The visualization is displayed in a block and a timeline in separated pictures.
\item The visualization parameters will be a nonempty subset of the parameters from the list below.
\item The visualization parameter includes the commit message.
\item The product is released open source and usable with the version of apache which is supported at release time.
\end{enumerate}
\section{May-Haves:}
\begin{enumerate}
\item The product has support for visualizing mercurial and subversion repositorys for a nonempty subset of the parameters, which is the same set as the set used in the must-haves.
\item The enduser is able to select which parameters he wants to influence the visualization on the website .
\item The enduser is able to select which parameter influences which part of the color.
\item The product website is responsive (e.g. by using Bootstrap) and works also with mobile clients. Is this context responsive means Bla
\item The user can upload a folder of a git repo instead of giving a URL.
\item The visualization is downloadable.
\item Share the visualization on instagram.
\item Can run with a basic LAMP environment.
\end{enumerate}
\section{Must-not-haves:}
\begin{enumerate}
\item The product has a desktop client.
\item The client supports version control systems other than mercurial, subversion and git.
\end{enumerate}
\section{Parameters:}
\begin{enumerate}
\item user
\item size of changes
\item only added sth.
\item only deleted sth.
\item time of day of commit
\item date of commit
\item commit message
\end{enumerate}
\end{document}