\documentclass[11pt]{scrartcl}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{color}	
\usepackage{calc}
\usepackage{enumitem}
\newcommand{\todo}[1]{\textbf{\textsc{\textcolor{red}{(TODO: #1)}}}}
\renewcommand{\baselinestretch}{1.0}\normalsize
\parindent 0pt
\author{Maike Maas \and Valerie Poser \and Sebastian Becking \and
        Marc Jose \and Fabian Kosmale \and Heiko Becker}
\title{Visualizing commit comments with chromograms}
\begin{document}
\maketitle

\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Frequency of use:}]
	\item[Use-case:] Visualizing an example repository 
	\item[Primary actor:] User of a desktop browser 
	\item[Goal in context:] Visualizing the repository in an overall block view with standard parameters 
	\item[Preconditions:] Browser with a working Internet connection
	\item[Trigger:] The user wants to get a visualization of an example repository

	\item[Scenario:]
		\begin{enumerate}[leftmargin=1.5em]
			\item The user opens the website and arrives at the home page.
			\item The user clicks on \enquote{JQuery}.
			\item The website enters the URL to the repository into the input field.
			\item The user clicks on \enquote{Visualize}.
			\item The website shows a progress bar with an informative text displayed beneath
				it. (See exception 1, 2)
			\item The website shows the repository's visualization.
			\item The user takes a screenshot to save the picture. 
		\end{enumerate}

	\item[Exceptions:]
		\begin{enumerate}[leftmargin=1.5em]
			\item The server hosting the repository does not respond $\rightarrow$ The
				website shows the homepage with an error message after timeout below the input 	
				field: 	\enquote{The Git repository is currently unavailable. Please try again later}.  
				(See use-case 7)
			\item The repository is too big $\rightarrow$  The server attempts to obtain a
				smaller copy of the repository by doing a shallow clone, containing only
				the 50 most recent commits. If the repository is still too big, the
				website shows the homepage with an error message after timeout below the input 	
				field: \enquote{The repository is too big. Please try another one}. (See use-case 8)
		\end{enumerate}

	\item[Priority:] high
	\item[Frequency of use:] Very often

\end{description}

\end{document}
