\documentclass[11pt]{scrartcl}
\usepackage{microtype}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{csquotes}
\usepackage{color}	
\usepackage{calc}
\usepackage{enumitem}
\newcommand{\todo}[1]{\textbf{\textsc{\textcolor{red}{(TODO: #1)}}}}
\renewcommand{\baselinestretch}{1.0}\normalsize
\parindent 0pt
\author{Maike Maas \and Valerie Poser \and Sebastian Becking \and
        Marc Jose \and Fabian Kosmale \and Heiko Becker}
\title{Visualizing commit comments with chromograms}
\begin{document}
\maketitle

\begin{description}[leftmargin=!,labelwidth=\widthof{\bfseries Frequency of use:}]
	\item[Use-case:] Visualizing a public Git repository 
	\item[Primary actor:] User of a desktop browser 
	\item[Goal in context:] Visualizing the repository in an overall block view with standard parameters 
	\item[Preconditions:] Browser with a working Internet connection and an URL to a Git repository
	\item[Trigger:] The user wants to get a visualization of his Git repository 

	\item[Scenario:]
		\begin{enumerate}[leftmargin=1.5em]
			\item The user opens the website and arrives at the home page.
			\item The user enters the URL to his Git repository. 
			\item The user clicks on \enquote{Visualize}. (See exception 1, 2, 3, 4, 5)
			\item The website shows a progress bar with an
				informative text displayed beneath
				it. (See exception 6, 7)
			\item The website shows the repository's visualization.
		\end{enumerate}
		
		
	\item[Alternate Flow:]
		\begin{enumerate}
			\item[2.1.a.] The user clicks on the button \enquote{Help}.
			\item[2.2.a.] The website overlays a help box with explaining texts and a link to the documentation.
			\item[2.3.a.] The user reads the helpful information and found a way to interact with the website.
			\item[2.4.a.] The user closes the help box.
			\item[] Return to Step 2 of the main scenario.
			\\
			\item[2.1.b.] The user clicks on the button in the upper right corner labeled with a book.
			\item[2.2.b.] The website opens the documentation page.
			\item[2.3.b.] The user reads the documentation and is informed.
			\item[2.4.b.] The user clicks on \enquote{return}.
			\item[] Return to Step 2 of the main scenario.
			\\
			\item[2.1.c.] The user clicks on \enquote{JQuery}.
			\item[2.2.c.] The website enters the URL into the input field.
			\item[2.3.c.] The user clicks on \enquote{Visualize}.
			\item[] Return to Step 4 of the main scenario.
			
		
		\end{enumerate}

	\item[Exception Flow:]
		\begin{enumerate}[leftmargin=1.5em]
			\item[E 1.] The URL is illegal
			\begin{enumerate}
				\item The website shows an error message below the input field: \enquote{You need to enter a legal link to a Git 						repository}.
				\item[] Return to Step 2 of the main scenario.
			\end{enumerate}
			
			\item[E 2.] The URL does not point to a Git repository. $\rightarrow$  The website
				shows an error message below the input field: \enquote{You need to enter a legal 		
				link to a git repository}.
				\begin{enumerate}
					\item The website shows an error message below the input field: \enquote{You need to enter a legal 		
						link to a git repository}.
					\item[] Return to Step 2 of the main scenario.
				\end{enumerate}
				
			\item[E 3.] The Repository is password protected
				\begin{enumerate}
					\item The website shows an
						error message below the input field: \enquote{The Git repository has to be without 
						password protection}.
					\item[] Return to Step 2 of the main scenario.
				\end{enumerate}
				
			\item[E 4.] The repository is protected by a private SSH key.
				\begin{enumerate}
					\item The website shows an error message below the input field: \enquote{The Git repository 
							has to be without SSH key protection}.
					\item[] Return to Step 2 of the main scenario.
				\end{enumerate}
				
			\item[E 5.] The repository is empty
				\begin{enumerate}
					\item  The website displays an error message below the input field: \enquote{The repository is empty}.
					\item[] Return to Step 2 of the main scenario.
				\end{enumerate}	
										
			\item[E 6.] The server hosting the repository does not respond.
				\begin{enumerate}
					\item Return to the home page.
					\item The website shows the homepage with an error message after timeout below the input 	
						field: 	\enquote{The Git repository is currently unavailable. Please try again later}.
					\item[] Return to Step 2 of the main scenario.
					
				\end{enumerate}
				
			\item[E 7.] The repository is too big.
				\begin{enumerate}
					\item Return to the home page.
					\item The server attempts to obtain a 
						smaller copy of the repository by doing a shallow clone, containing only
						the 50 most recent commits. If the repository is still too big, the
						website shows the homepage with an error message after timeout below the input 	
						field: \enquote{The repository is too big. Please try another one}.
					\item[] Return to Step 2 of the main scenario.
				\end{enumerate}
		\end{enumerate}

	\item[Priority:] high
	\item[Frequency of use:] Very often --- this is the main functionality of the system

\end{description}

\end{document}
